Opening a Cold Case \\ {\large Investigating how Temperature Affects The Rate of Robberies}

### 2014-12-02 stat374/hw4.tex
Done hw4

                So we may conclude \(\E(F)=F_0\). Additionally, 
                        \var(F(x)) &= \E(F(x)^2) - \E(F(x))^2 \\
                        \var(F(x)) &= \var\left(\sumj w_jI_{\{z\leq s_j\}}(x)\right) \\
                        \var(F(x)) &= \E(F(x)^2) - \E(F(x))^2 \\
                        \var(F(x)) &= \E\left(\left(\sumj w_jI_{\{z\leq s_j\}}(x)\right)^2\right) - F_0(x)^2 \\
                        \var(F(x)) &= \sumj\sumk \E\left(w_jw_kI_{\{z\leq s_j\}}(x)I_{\{z\leq s_k\}}(x)\right) - F_0(x)^2 

@@

>>>>

                So we may conclude \(\E(F)=F_0\). To see that the prior gets more concentrated around $F_0$ as $\alpha$ increases, we only need demonstrate that the probability the drawn distribution cumulative distribution function function differs by more than $\epsilon$ from $F_0$ is decreasing as $\alpha$ increases. To do this, we note that this probability is the sum of the probabilities that the difference is achieved in exactly a certain number of steps of the stick break algorithm. This probability, conditioned on a particular sum of weights, decreases as the sum of weights decreases. Thus, since the probability of a partial sum of weights having reached a particular length decreases with $\alpha$ (as the expected size of the weights decreases), the probability of the difference occurring in a particular number of steps decreases as well, and in turn the probability of achieving that difference in any number of steps.

@@

                \item[(d)] These are my plots:
                    \begin{center}
                        \includegraphics[width=9cm]{hw4/5_d} 
                    \end{center}
                \item[(e)] 
                    \begin{itemize}
                        \item[i.] These are the plots, for $\alpha=100$ \\
                            \includegraphics[width=9cm]{hw4/5_ei10} 
                            \includegraphics[width=9cm]{hw4/5_ei25}  \\
                            \includegraphics[width=9cm]{hw4/5_ei100}
                    \end{itemize}[i.] These are the plots of the posteriors, their CIs, and the draws from them, with $\alpha=100$ \\
                            \includegraphics[width=9cm]{hw4/5_eii10} 
                            \includegraphics[width=9cm]{hw4/5_eii25}  \\
                            \includegraphics[width=9cm]{hw4/5_eii100}
        \end{itemize}
